%------------------------------------
% Dario Taraborelli
% Typesetting your academic CV in LaTeX
%
% URL: http://nitens.org/taraborelli/cvtex
% DISCLAIMER: This template is provided for free and without any guarantee
% that it will correctly compile on your system if you have a non-standard
% configuration.
% Some rights reserved: http://creativecommons.org/licenses/by-sa/3.0/
%------------------------------------

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[11pt, letterpaper]{article}
\usepackage{fontspec}

% DOCUMENT LAYOUT
\usepackage{geometry}
\geometry{a4paper, textwidth=5.5in, textheight=8.5in, marginparsep=7pt, marginparwidth=.6in}
\setlength\parindent{0in}

% FONTS
\usepackage{xunicode}
\usepackage{xltxtra}
\defaultfontfeatures{Mapping=tex-text} % converts LaTeX specials (``quotes'' --- dashes etc.) to unicode
\setromanfont [Ligatures={Common}, Numbers={OldStyle}]{Hoefler Text}
\setmonofont[Scale=0.8]{Monaco}
\setsansfont[Scale=0.9]{Optima Regular}
% ---- CUSTOM AMPERSAND
\newcommand{\amper}{{\fontspec[Scale=.95]{Hoefler Text}\selectfont\itshape\&}}
% ---- MARGIN YEARS
\usepackage{marginnote}
\newcommand{\years}[1]{\marginnote{\scriptsize #1}}
\renewcommand*{\raggedleftmarginnote}{}
\setlength{\marginparsep}{7pt}
\reversemarginpar

% HEADINGS
\usepackage{sectsty}
\usepackage[normalem]{ulem}
\sectionfont{\sffamily\mdseries\large\underline}
\subsectionfont{\rmfamily\mdseries\scshape\normalsize}
\subsubsectionfont{\rmfamily\bfseries\upshape\normalsize}
\usepackage{multicol}

% BIBTEX
\usepackage{bibentry} % must have natbib package installed
% \newcites{first-author}{Journal articles, first author}
% \newcites{co-author}{Journal articles, co-author}
% \newcites{conf}{Conference Proceedings}
% \newcites{present}{Conference Presentations}
% \newcites{press}{Press}

% For setting item spacing
\usepackage{enumitem}
\setlist{noitemsep}

% PDF SETUP
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR
\makeatletter\let\saved@bibitem\@bibitem\makeatother
\usepackage[xetex, bookmarks, colorlinks, breaklinks, pdftitle={Daniel B. Goodman - vita},pdfauthor={Daniel Goodman}]{hyperref}
\makeatletter\let\@bibitem\saved@bibitem\makeatother
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=blue}

%% PUBLICATIONS, ETC. - takes two arguments; the first is the year of
%%%% publication and the second is the bibtex label

%% http://tex.stackexchange.com/questions/18664/underline-my-name-in-the-bibliography
\newcommand{\myname}[1]{\textit{#1}}

\newcommand{\publication}[2]{\vbox{
\years{#1} \bibentry{#2}. \par\vspace{0.8mm}
}}

\newcommand{\cd}{$\cdot${ }}


% DOCUMENT
\begin{document}

\nobibliography{citations_w_bold}

\textsf{\LARGE Daniel Bryan Goodman}\\[1cm]
\begin{multicols}{2}
Wyss Institute for Bioinspired \mbox{Engineering}\\
528-3C Center for Life Sciences\\
3 Blackfan Circle\\
Boston, MA \texttt{02115}
U.S.A.\\[.2cm]

Phone: \texttt{617-459-2949}\\
email: \href{mailto:dbg@mit.edu}{dbg@mit.edu}\\
\textsc{url}: \href{http://www.dbgoodman.com/}{http://www.dbgoodman.com/}\\
\end{multicols}

%%\hrule
\section*{Current position}
\emph{PhD Candidate}, Harvard-MIT Division of Health Science and Technology, Masschusetts Institute of Technology. \emph{Expected graduation: May, 2015}
\\[2mm]
\emph{Hometown Media Outlet: Orange County Register}

%%\hrule
\section*{Academic Background}

\years{2015}\textsc{PhD} in Medical Engineering and Medical Physics, Massachusetts Institute of Technology. Cambridge, MA, USA. \\

\noindent\years{2008-2009}Whitaker International Bioengineering Fellow, University of Cambridge. Cambridge, UK.\\

\noindent\years{2008}\textsc{BS} in Bioengineering w/ specialization in Bioinformatics, University of California at San Diego. La Jolla, CA, USA.\\


%%\hrule
\section*{Research Experience}

\noindent\years{2010-}
\emph{Doctoral Thesis Research:} Department of Genetics, Harvard Medical School. Boston, MA. (advisor: Dr. George M. Church)
\begin{itemize}
	\item Multiplexed characterization of genetic regulatory elements using novel high-throughput fluorescent quantitation technique
	\item Identified RNA secondary structure as major determinant of 5' codon bias in bacterial genomes, implications for improved codon optimization
    \item Developed cloud-based software for high-throughput bacterial genome analysis and engineering
    \item Multiplexed design, synthesis, and measurement of synthetic gene regulatory networks for optimized molecular sensors\\[5mm]
\end{itemize}

\noindent\years{2011}
Harvard University, MA. International Genetically Engineered Machine Competition. (advisor: Dr. George M. Church)
\begin{itemize}
    \item Led a team of undergraduate students to designed and synthesize fifty-thousand zinc finger monomers from a printed oligonucleotide array
    \item Developed a novel selection system to test fingers in multiplex using a two-hybrid system in E. coli
\end{itemize}

\noindent\years{2008-2009}
University of Cambridge, UK. Whitaker International Bioengineering Fellowship. (advisor: Dr. Simon Tavaré)
\begin{itemize}
    \item Built microfluidics platform to automate sequential oligo-probe DNA sequencing
    \item Wrote image analysis software in C++/R/Matlab to analyze terabytes of fluorescent bead image data
    \item Developed a novel experimental method for identifying methylation patterns in single cells using emulsion PCR, fluorescent microscopy, and image analysis
\end{itemize}

\noindent\years{2008}
University of Cambridge, UK. International Genetically Engineered Machine Competition, University of Cambridge Team.  (advisors: Drs. Jim Haseloff, Gos Micklem, Jim Ajioka)
\begin{itemize}
    \item Led a team of undergraduate engineers, mathematicians, biologists
    \item Designed and built a two-component signaling system to produce spatial patterning using standardized genetic parts
\end{itemize}

\noindent\years{2005-2008}
\emph{Undergraduate Thesis Research:} University of California, San Diego. (advisor: Dr. Pavel Pevzner)
\begin{itemize}
    \item Developed algorithm to determine evolutionary relationships of small genomes based on paralogous gene ordering; improved phylogeny of baculoviruses
    \item Developed software tools to validate genome annotations via comparative genomics and mass spectrometry data
\end{itemize}

\noindent\years{2007-2008}
\emph{Undergraduate Thesis Research:} RSCB Protein Data Bank, San Diego, CA. (advisors: Drs. Phillip E. Bourne and Lei Xie.)
\begin{itemize}
    \item Functional site characterization/analysis, mining data from Protein Data Bank
    \item Used protein docking software (DOCK, Autodock) to identify binding profiles
    \item Profiles analyzed to find potential off-site targets for major pharmaceuticals
    \item Presented work at ISMB 2007 in Vienna, Austria
\end{itemize}

\noindent\years{2006}
Osaka University, Osaka, Japan. (advisors: Drs. Shinji Shimojo and Phillip E. Bourne)
\begin{itemize}
    \item Used automated docking software (DOCK) in a Grid environment
    \item Performed virtual ligand screening on a novel human kinase target
    \item Developed distributed software framework to interface with DOCK
    \item Presented research at Supercomputing 2006\\[5mm]
\end{itemize}

\noindent\years{2004-2006}
University of California, Irvine. (advisor: Dr. Abraham P. Lee)
\begin{itemize}
    \item Conducted microfluidics impedence-based cell-sensing experiments
    \item Designed and fabricated microfluidic devices in a cleanroom environment
    \item Assembled hardware for microfluidic flow control
    \item Wrote software for microfluidic device data acquisition
\end{itemize}

\noindent\years{2004-2006}
Google Summer of Code. (advisor: Shankar Subramaniam)
\begin{itemize}
    \item Created an online unified searchable database of gene and protein homology data
    \item Released the source code on the open-source community SourceForge
\end{itemize}


%\hrule
\section*{Honors \amper{} awards}

\noindent\years{2012}SynBERC Practices Fellow, Six Parties Synthetic Biology Symposium\\

\noindent\years{2009-2014}National Science Foundation Graduate Research Fellowship\\

\noindent\years{2008-2009}Whitaker International Bioengineering Fellow\\

\noindent\years{2006}Pacific Rim Undergraduate Experience (PRIME) Award Recipient\\

\noindent\years{2005}Project Showcase, Google Summer of Code\\

\noindent\years{2003-2007}Provost Honors, Eleanor Roosevelt College at UCSD
\section*{Publications \& talks}

\subsection*{Journal articles}
\noindent

\publication{2014}{gregg2014rational}

\publication{2013}{lajoie2013genomically}

\publication{2013}{goodman2013causes}

\publication{2013}{kosuri2013composability}

\publication{2007}{goodman2007baculovirus}

\publication{2011}{isaacs2011precise}

\publication{2009}{tiemann2009product}

\publication{2008}{gupta2008comparative}

\subsection*{Journal articles submitted/in preparation}
\noindent

\publication{(2015)}{goodman2015millstone}

\publication{(2015)}{kuznetsov2015recoli}

\subsection*{Conference proceedings}
\noindent

\publication{2005}{lee2005m3}

\publication{2004}{lee2004nanochannel}

\subsection*{Conference Presentations}
\noindent

\publication{2014}{goodman2014talk-synberc-millstone}

\publication{2013}{goodman2013talk-wyss-synthesis}

\publication{2013}{goodman2013talk-sb6-composability}

\publication{2012}{goodman2012talk-synberc-synthesis}

\publication{2008}{goodman2008talk-igem}

\publication{2007}{goodman2007talk-ismb}

\publication{2006}{goodman2006talk-baculo}

\publication{2006}{goodman2006talk-docking}

\subsection*{Press/Media}
\noindent

\publication{2013}{press2013science_podcast}

\publication{2013}{press2013getsynbio}

\publication{2011}{press2011nyt_recoli}

\publication{2008}{press2008leading_edge}

\section*{Teaching}
\noindent

\noindent\years{2011}Head Teaching Fellow, International Genetically Engineered Machines (iGEM) Team, Harvard University\\

\noindent\years{2007-2008}Salk Mobile Science Laboratory\\

\noindent\years{2007}Biology Teaching Assistant, University of California at San Diego.\\

%\vspace{1cm}
\vfill{}
%\hrulefill

\begin{center}
{\scriptsize  Last updated: \today\- •\- Typeset in \href{http://nitens.org/taraborelli/cvtex}{
\fontspec{Times New Roman}\XeTeX }\\
% ---- FILL IN THE FULL URL TO YOUR CV HERE
Papers, source code, and more information about past
research can be found at my website:
\href{http://www.dbgoodman.com}{http://www.dbgoodman.com}}
\end{center}

\bibliographystyle{plain}

\end{document}